The shape of dark matter halos in the AURIGA simulations

### 2019-02-20 Paper/paper.tex
edit

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/halo16.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile} \label{fig:triaxial_radius}
\end{figure*}

@@

Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circles while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center gives rise to perturbed axial ratio measurements. 
Figure \ref{fig:triax_MHD} shows the same information, this time for
the MHD simulations. 
In this case, the main radial trend continues to hold, albeit less
pronounced.
We also find that halos in MHD simulations are in general rounder than
their DM counterparts

@@

\begin{figure*}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations.
   Each dot represents the shape characterization of each halo at the
   2 times the virial radius and a  1/16 fraction of the virial radius
   differentiated by color. 
   Errorbar shows median and errors for each sampled radii. 
   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!)}}
  \label{fig:triax_DM_MHD}
\end{figure*}

@@

We have now established that DM-only have a steady and monotonous
trend towards larger sphericity with increasing radius. 
This radial trend is mimicked when the shape is measured at the virial
radius as a function of cosmic time.
The halo should become rounder with decreasing redshift, this is
expected by the continuous influence of the gravitational potential on
a collisionless fluid \citep{Vera-Ciro_et_al._2011}.

\begin{figure*}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
  \caption{Radial profile at $z=0$ (dashed line) and 
    the istorical profile at virial radius R500 (colour line). Example
    of a halo where there is some correlation between these two
    profiles, as usually happens for DM only
    simulations. Conclusion: DM only halos usually (fraction?) have
    correlated shape profiles. {\bf Aqui la idea es mostrar el mismo
      halo, no halos diferentes!}} 
  \label{fig:DM Z Triax}
\end{figure*}

\begin{figure}
  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in
    terms of redshift (color). This halo maintains its shape until
    $z\approx 1$ obviating the systematic rounding effect in time from
    asymmetric potentials. Each plot-line represents the radial
    profile at a determined redshift. Conclussion: Mainly for b/a, it increases for:
    (1) for bigger radii (fixed redshift)(2) for lower redshift (fixed
    radius) It explains the correlation between radial profile and
    history, but does not require that curves match in the triaxial
    plane.}
  \label{fig:RedshiftGood}
\end{figure}

Interestingly, these two parametic plots i.e. $(b/a,c/a)(z=0,r)$ and
$(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos
\ref{fig:DM Z Triax}. This means that, for DM-only halos, one can
approximate its shape at higher redshift by simply sampling its
current shape at a smaller radius \textbf{wording}. This relationship
relies strongly on the steady and monotonous tendency of DM halos
towards sphericity for bigger radii and smaller redshift.

MHD halos, on the other hand, do not exhibit tendency towards
sphericity with bigger radii, but they do get sistematically rounder
at lower redshift as seen in figure \ref{fig:RedshiftGood}. This
effectively vanishes this correlation as seen from a DM halo
\ref{fig:MHD Z Triax}.

\begin{figure}

  \caption{MHD. Radial profile at redshift 0 (dashed line)
    Historical profile at virial radius R500 (colour line)
    Example of a halo where there is no correlation
    between these two profiles, as usually happens in
    MHD. Conclusion: MHD halos usually (fraction?) have uncorrelated shape profiles.}
    \label{fig:MHD Z Triax} 
\end{figure}

Better graphics.

>>>>

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/halo16.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile. {\bf Aqui hay que quiar c/b,
    no es relevante}} \label{fig:triaxial_radius}
\end{figure*}

@@

Figure \ref{fig:triax_DM_MHD} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circles while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center gives rise to perturbed axial ratio measurements. 
The right panel on Figure \ref{fig:triax_DM_MHD} shows the same information, this time for
the MHD simulations. 
In this case, the main radial trend continues to hold, albeit less
pronounced.
We also find that halos in MHD simulations are in general rounder than
their DM counterparts

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo at the
   2 times the virial radius and a  1/16 fraction of the virial radius
   differentiated by color. 
   Errorbar shows median and errors for each sampled radii. 
   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!)}}
  \label{fig:triax_DM_MHD}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
  \caption{Radial profile at $z=0$ (dashed line) and 
    the historical profile at the virial radius (colour line). 
    Results for DM simulations on the left, for MHD on the right.
    {\bf Aqui la idea es mostrar el mismo
      halo, no halos diferentes!}} 
  \label{fig:redshift_triaxial}
\end{figure*}

\begin{figure*}
  \subfloat[halo 16 DM]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \subfloat[halo 16 MHD]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in
    terms of redshift (color). This halo maintains its shape until
    $z\approx 1$ obviating the systematic rounding effect in time from
    asymmetric potentials. Each plot-line represents the radial
    profile at a determined redshift. Conclussion: Mainly for b/a, it increases for:
    (1) for bigger radii (fixed redshift)(2) for lower redshift (fixed
    radius) It explains the correlation between radial profile and
    history, but does not require that curves match in the triaxial
    plane. {\bf En esta grafica el panel de abajo deberia ser la triaxialidad.}}
  \label{fig:RedshiftGood}
\end{figure*}

We know that DM-only have a steady and monotonous
trend towards larger sphericity with increasing radius. 
This radial trend is mimicked when the shape is measured at the virial
radius as a function of cosmic time.
The halo should become rounder with decreasing redshift, this is
expected by the continuous influence of the gravitational potential on
a collisionless fluid \citep{Vera-Ciro_et_al._2011}.

We show in the left panel of Figure \ref{fig:redshift_triaxial} an
example with this effect in Halo 27 of the DM simulations:
the radial triaxiality at $z=0$ and the historical triaxiality at
$R_{\rm vir}$ are correlated. 
The right panel on the same Figure \ref{fig:redshift_triaxial}
illustrates how this correlation is absent in MHD simulations.

This means that for DM-only halos one can approximate its shape at
higher redshift by simply sampling its 
current shape at a smaller radius. 
This correlation seems to be prompted by the continous inside-out
build-up of the dark matter halo; baryonic effects seem to jeopardize
the apparent smoother growth in DM-only simulations.
